---
title: "Viz_part_01"
author: "Matthew Ma"
output: github_document
---

## Lets import data

```{r}
library(tidyverse)
library(ggridges)
```

This code from the the visualization module

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Lets make a scatterplot

```{r}

ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()

```


## Lets make the same scatterplot, but different.

```{r}

weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

```

## Lets keep making the same plot, but different.

```{r}

weather_scatterplot =
  weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_scatterplot +
  geom_point()

```


## lets fancy this up

```{r}

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)

```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) + 
  geom_smooth()

```


## Lets split up 'tmin' and 'tmax'

```{r}

weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = 0.3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Some quick stuff

```{r}

weather_df %>% 
  ggplot(aes( x = tmax, y = tmin)) +
  geom_hex()
```

## Univariate plots

Histograms, barplots, boxplots, violins, etc..

```{r}

weather_df %>% 
  ggplot(aes( x = tmax, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)

```


## Lets see more options

```{r}

weather_df %>% 
  ggplot(aes( x = tmax, fill = name)) +
  geom_density(alpha = .3)

```

## Lets do boxplot

```{r}

weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_boxplot() +
  facet_grid(. ~ name)

```


## Violin?

```{r}

weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_violin()

```

OR ridgeplots

```{r}

weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()

```

## Saving and embedding plots

First --  lets save a plot

```{r}

weather_scatterplot = 
  weather_df %>% 
  ggplot(aes( x = date, y = tmax, color = name)) +
  geom_point(aes( size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)

weather_scatterplot

ggsave(file = 
         "results/weather_scatterplot.pdf", 
       plot = weather_scatterplot,
       width = 8, height = 5)

```


